\newpage



%\setcounter{section}{1}  
%\setcounter{page}{1}

\section{References cited}

\begin{thebibliography}{200}


\bibitem{RISAC}
{\em Scientific Opportunities with a Rare-Isotope Facility in the {United
  States}}. The National Academies Press, 2007.

\bibitem{Decadal2012}
{\em Nuclear Physics: Exploring the Heart of Matter}. The National Academies
  Press, 2012.

\bibitem{jacekwitek1998}
J.~Dobaczewski and W.~Nazarewicz.
\newblock {\em Phil. Trans. R. Soc. Lond. A}, 356:2007, 1998.

\bibitem{thoennessen2011}
M.~Thoennessen and B.~Sherrill.
\newblock From isotopes to the stars.
\newblock {\em Nature}, 473:25--26, 2011.

\bibitem{brown2001}
B.A. Brown.
\newblock The nuclear shell model towards the drip lines.
\newblock {\em Prog.~Part.~Nucl.~Phys.}, 47:517, 2001.

\bibitem{michael2012}
T~Baumann, A~Spyrou, and M~Thoennessen.
\newblock Nuclear structure experiments along the neutron drip line.
\newblock {\em Rep.~Prog.~Phys.}, 75:036301, 2012.

\bibitem{sorlin2008}
O.~Sorlin and M.~G. Porquet.
\newblock {\em Prog.~Part.~Nucl.~Phys.}, 61:602, 2008.

\bibitem{witeknature2012}
J.~Erler, N.~Birge, M.~Kortelainen, W.~Nazarewicz, E.~Olsen, A.~M. Perhac, and
  M.~Stoitsov.
\newblock {\em Nature}, 486:509, 2012.

\bibitem{UNEDF}
G.~F. Bertsch, D.~J. Dean, and W.~Nazarewicz.
\newblock {\em SciDAC Review}, 6:42, 2007.

\bibitem{shavittbartlett2009}
I.~Shavitt and R.~J. Bartlett.
\newblock {\em Many-body Methods in Chemistry and Physics}.
\newblock Cambridge University Press, 2009.

\bibitem{helgaker}
T.~Helgaker, P.~J{\o}rgensen, and J.~Olsen.
\newblock {\em Molecular Electronic Structure Theory. Energy and Wave
  Functions}.
\newblock Wiley, Chichester, 2000.

\bibitem{hagen2010a}
G.~Hagen, T.~Papenbrock, D.~J. Dean, and M.~Hjorth-Jensen.
\newblock Ab initio coupled-cluster approach to nuclear structure with modern
  nucleon-nucleon interactions.
\newblock {\em Phys.~Rev.~C}, 82(3):034330, 2010.

\bibitem{pieper2001a}
Steven~C. Pieper and R.~B. Wiringa.
\newblock {Quantum Monte Carlo calculations of light nuclei}.
\newblock {\em Annual Review of Nuclear and Particle Science}, 51(1):53--90,
  2001,
  http://www.annualreviews.org/doi/pdf/10.1146/annurev.nucl.51.101701.132506.

\bibitem{kdl1997}
S.E. Koonin, D.J. Dean, and K.~Langanke.
\newblock Shell model monte carlo methods.
\newblock {\em Phys.~Rep.}, 278:1, 1997.

\bibitem{utsuno1999}
Yutaka Utsuno, Takaharu Otsuka, Takahiro Mizusaki, and Michio Honma.
\newblock Varying shell gap and deformation in n ~ 20 unstable nuclei studied
  by the monte carlo shell model.
\newblock {\em Phys.~Rev.~C}, 60:054315, 1999.

\bibitem{hjorthjensen1995}
Morten Hjorth-Jensen, Thomas~T.S. Kuo, and Eivind Osnes.
\newblock Realistic effective interactions for nuclear systems.
\newblock {\em Phys.~Rep.}, 261:125, 1995.

\bibitem{dickhoff}
W.~H. Dickhoff and D.~Van Neck.
\newblock {\em Many-Body Theory exposed!}
\newblock World Scientific, 2005.

\bibitem{barbieri2004}
C.~Barbieri and W.~H. Dickhoff.
\newblock Self-consistent green's function method for nuclei and nuclear
  matter.
\newblock {\em Prog.~Part.~Nucl.~Phys.}, 52:377, 2004.

\bibitem{roth2005}
R.~Roth, H.~Hergert, P.~Papakonstantinou, T.~Neff, and H.~Feldmeier.
\newblock Matrix elements and few-body calculations within the unitary
  correlation operator method.
\newblock {\em Phys.~Rev.~C}, 72:034002, 2005.

\bibitem{white1992}
S.~R. White.
\newblock Density matrix formulation for quantum renormalization groups.
\newblock {\em Phys.~Rev.~Lett.}, 69:2863--2866, 1992.

\bibitem{schollwock2005}
U.~Schollwock.
\newblock The density-matrix renormalization group.
\newblock {\em Rev.~Mod.~Phys.}, 77:259, 2005.

\bibitem{rotureau2009}
J.~Rotureau, N.~Michel, W.~Nazarewicz, M.~P\l{}oszajczak, and J.~Dukelsky.
\newblock Density matrix renormalization group approach to two-fluid open
  many-fermion systems.
\newblock {\em Phys.~Rev.~C}, 79:014304, 2009.

\bibitem{bartlett2005}
R.~J. Bartlett, V.~F. Lotrich, and I.~V. Schweigert.
\newblock Ab initio density functional theory: The best of both worlds?
\newblock {\em J.~Chem.~Phys.}, 123:062205, 2005.

\bibitem{tsukiyama2011}
K.~Tsukiyama, S.~K. Bogner, and A.~Schwenk.
\newblock In-medium similarity renormalization group for nuclei.
\newblock {\em Phys. Rev. Lett.}, 106:222502, 2011.


\bibitem{hergert2012}
H.~Hergert, S.K. Bogner, S.~Binder, A.~Calci, J.~Langhammer, et~al.
\newblock {In-Medium Similarity Renormalization Group with Chiral Two- Plus
  Three-Nucleon Interactions}.
\newblock {\em Phys.Rev.}, C87:034307, 2013.

\bibitem{nushellx}  NuShellX program at MSU, B. A. Brown, W. D. M. Rae, E. McDonald and M. Horoi,
\url{http://www.nscl.msu.edu/˜brown/resources/resources.html}.



\bibitem{caurier2005}
E.~Caurier, G.~Martinez-Pinedo, F.~Nowacki, A.~Poves, and A.~P. Zuker.
\newblock The shell model as a unified view of nuclear structure.
\newblock {\em Rev.~Mod.~Phys.}, 77:427, 2005.

\bibitem{navratil2009}
Petr Navr{\'a}til, Sofia Quaglioni, Ionel Stetcu, and Bruce~R Barrett.
\newblock Recent developments in no-core shell-model calculations.
\newblock {\em J.~Phys.~G}, 36:083101, 2009.




\bibitem{dean2004}
D.~J. Dean, T. Engeland, M.~Hjorth-Jensen, M.~Kartamyshev, and E.~Osnes
\newblock Effective Interactions and the Nuclear Shell Model
\newblock {\em Prog.~Part.~Nucl.~Phys.}, 54:419, 2004.


\bibitem{Bergli2011}
Elise Bergli and Morten Hjorth-Jensen.
\newblock { Summation of Parquet diagrams as an {\em ab initio} method in
  nuclear structure calculations}.
\newblock {\em Annals of Physics}, 326:1125, 2011.

\bibitem{tsukiyama2012}
K.~Tsukiyama, S.K. Bogner, and A.~Schwenk.
\newblock {In-Medium Similarity Renormalization Group for Open-Shell Nuclei}.
\newblock {\em Phys.Rev.}, C85:061304, 2012.

\bibitem{reimann2013} S.~Reimann, J.~H\o gberget, S.~K.~Bogner, and M.~Hjorth-Jensen, 
\newblock {In-Mediun SRG calculations for Parabolic Quantum Dots}, 
\newblock {\em Physical Review B}, in preparation.


\bibitem{mhj2013g} G. Baardsen, A.\ Ekstr\"om, G.\ Hagen, and M.\ Hjorth-Jensen,
\newblock { Coupled-cluster studies of infinite  nuclear matter}, 
\newblock {\em Physical Review C},  88: in press (2013) and arXiv1306.5681



\bibitem{mhj2013i} G.~Hagen, T.~Papenbrock,   A.~Ekstr\"om, G.~Baardsen, S.~Gandolfi, M.~Hjorth-Jensen, C.~Horowitz and K.~A.~Wendt,
\newblock { Coupled-cluster calculations of nucleonic matter}, 
\newblock {\em Physical Review C},  submitted.


\bibitem{mhj2013j}  T.~Papenbrock, G.~Hagen, M.~Hjorth-Jensen, and  D.~J.~Dean, 
\newblock { Coupled-cluster computations of atomic nuclei}, 
\newblock {\em Reports on Progress in Physics},  commissioned and submitted November 2013.


\bibitem{mhj2011c}
Magnus Pedersen Lohne, Gaute Hagen, Morten Hjorth-Jensen, Simen Kvaal, and Francesco Pederiva,
\newblock { Ab initio calculations of Circular quantum dots}.
\newblock {\em Physical Review B}, 84:032501, 2011.


\bibitem{alavi1} Booth, G. H. and Gr\"uneis, A. and Kresse, G.  and Alavi, A.,
\newblock {Towards an exact description of electronic wavefunctions in real
	solids}, 
\newblock {\em Nature}, 493:365 2013


\bibitem{alavi2} Booth, G. H.  and  Thom, A. J. W. and Alavi, A., 
\newblock {Fermion Monte Carlo without fixed nodes: A game of life, death, and annihilation in S
later determinant space },
\newblock {\em J. Chem. Phys.}, 131:054106 2009.

\bibitem{alavi3}  Shepherd, J. J.  and Booth, G. H.  and Alavi, A.,
\newblock {Investigation of the full configuration interaction quantum Monte Carlo method using 
homogeneous electron gas models },
\newblock {\em J. Chem. Phys.}, 136:244101 2012


\bibitem{alavi4} Shepherd, J. J. and Booth, G. H. and Gr\"uneis, A. and Alavi, A.,
\newblock { Full configuration interaction perspective on the homogeneous electron
	gas },
\newblock {\em Phys. Rev. B}, 85:081103 2012



\bibitem{alavi5} Shepherd, J. J. and Gr\"uneis, A. and Booth, G. H. and Kresse, G. and Alavi, A.,
\newblock { Convergence of many-body wave-function expansions using a plane-wave
	basis: From homogeneous electron gas to solid state systems },
\newblock {\em Phys. Rev. B}, 86:035111 2012




\bibitem{baardsen2013} G.~Baardsen, K.~Leikanger, S.~Reimann, S.~K.~Bogner, and M.~Hjorth-Jensen, 
\newblock {First Principle Calculations for the two-dimensional Homogeneous Electron Gas}, 
\newblock {\em Physical Review B}, in preparation.

\bibitem{Bender:2003jk}
Michael Bender, Paul-Henri Heenen, and Paul-Gerhard Reinhard.
\newblock Self-consistent mean-field models for nuclear structure.
\newblock {\em Rev. Mod. Phys.}, 75:121--180, 2003.



\bibitem{burrows2013}
Adam Burrows.
\newblock \textit{Colloquium} : Perspectives on core-collapse supernova theory.
\newblock {\em Rev. Mod. Phys.}, 85:245--261, Feb 2013.

\bibitem{weber1999}
F.~Weber.
\newblock {\em Pulsars as Astrophysical Laboratories for Nuclear and Particle
  Physics}.
\newblock Institute of Physics Publishing, London, 1999.

\bibitem{hh2000}
H.~Heiselberg and M.~Hjorth-Jensen.
\newblock Phases of dense matter in neutron stars.
\newblock {\em Phys. Rep.}, 328:237, 2000.

\bibitem{lattimer2007}
J.~M. Lattimer and M.~Prakash.
\newblock Neutron star observations: Prognosis for equation of state
  constraints.
\newblock {\em Phys. Rep.}, 442:109, 2007.

\bibitem{sammarruca2010}
Francesca Sammarruca.
\newblock The microscopic approach to nuclear matter and neutron star matter.
\newblock {\em International Journal of Modern Physics E}, 19(07):1259--1313,
  2010.

\bibitem{lattimer2012}
J.~M. Lattimer.
\newblock The nuclear equation of state and neutron star masses.
\newblock {\em Ann. Rev. Nucl. Part. Science}, 62:485, 2012.

\bibitem{hebeler2012f}
K.~Hebeler, J.~M. Lattimer, C.~J. Pethick, and A.~Schwenk.
\newblock Equation of state and neutron star properties constrained by nuclear
  physics and observation.
\newblock {\em Astrophys. J.}, 773:11, 2013.

\bibitem{brown2000}
B.~Alex~Brown.
\newblock Neutron radii in nuclei and the neutron equation of state.
\newblock {\em Phys. Rev. Lett.}, 85:5296--5299, Dec 2000.

\bibitem{horowitz2001}
C.~J. Horowitz and J.~Piekarewicz.
\newblock Neutron star structure and the neutron radius of $^{208}pb$.
\newblock {\em Phys. Rev. Lett.}, 86:5647--5650, Jun 2001.

\bibitem{shlomo1993}
S.~Shlomo and D.~H. Youngblood.
\newblock Nuclear matter compressibility from isoscalar giant monopole
  resonance.
\newblock {\em Phys. Rev. C}, 47:529--536, Feb 1993.

\bibitem{abrahamyan2012}
S.~Abrahamyan, Z.~Ahmed, H.~Albataineh, K.~Aniol, D.~S. Armstrong,
  W.~Armstrong, T.~Averett, B.~Babineau, A.~Barbieri, V.~Bellini,
  R.~Beminiwattha, J.~Benesch, F.~Benmokhtar, T.~Bielarski, W.~Boeglin,
  A.~Camsonne, M.~Canan, P.~Carter, G.~D. Cates, C.~Chen, J.-P. Chen, O.~Hen,
  F.~Cusanno, M.~M. Dalton, R.~De~Leo, K.~de~Jager, W.~Deconinck, P.~Decowski,
  X.~Deng, A.~Deur, D.~Dutta, A.~Etile, D.~Flay, G.~B. Franklin, M.~Friend,
  S.~Frullani, E.~Fuchey, F.~Garibaldi, E.~Gasser, R.~Gilman, A.~Giusa,
  A.~Glamazdin, J.~Gomez, J.~Grames, C.~Gu, O.~Hansen, J.~Hansknecht, D.~W.
  Higinbotham, R.~S. Holmes, T.~Holmstrom, C.~J. Horowitz, J.~Hoskins,
  J.~Huang, C.~E. Hyde, F.~Itard, C.-M. Jen, E.~Jensen, G.~Jin, S.~Johnston,
  A.~Kelleher, K.~Kliakhandler, P.~M. King, S.~Kowalski, K.~S. Kumar,
  J.~Leacock, J.~Leckey, J.~H. Lee, J.~J. LeRose, R.~Lindgren, N.~Liyanage,
  N.~Lubinsky, J.~Mammei, F.~Mammoliti, D.~J. Margaziotis, P.~Markowitz,
  A.~McCreary, D.~McNulty, L.~Mercado, Z.-E. Meziani, R.~W. Michaels,
  M.~Mihovilovic, N.~Muangma, C.~Mu\~noz Camacho, S.~Nanda, V.~Nelyubin,
  N.~Nuruzzaman, Y.~Oh, A.~Palmer, D.~Parno, K.~D. Paschke, S.~K. Phillips,
  B.~Poelker, R.~Pomatsalyuk, M.~Posik, A.~J.~R. Puckett, B.~Quinn, A.~Rakhman,
  P.~E. Reimer, S.~Riordan, P.~Rogan, G.~Ron, G.~Russo, K.~Saenboonruang,
  A.~Saha, B.~Sawatzky, A.~Shahinyan, R.~Silwal, S.~Sirca, K.~Slifer,
  P.~Solvignon, P.~A. Souder, M.~L. Sperduto, R.~Subedi, R.~Suleiman,
  V.~Sulkosky, C.~M. Sutera, W.~A. Tobias, W.~Troth, G.~M. Urciuoli,
  B.~Waidyawansa, D.~Wang, J.~Wexler, R.~Wilson, B.~Wojtsekhowski, X.~Yan,
  H.~Yao, Y.~Ye, Z.~Ye, V.~Yim, L.~Zana, X.~Zhan, J.~Zhang, Y.~Zhang, X.~Zheng,
  and P.~Zhu.
\newblock Measurement of the neutron radius of $^{208}\mathrm{Pb}$ through
  parity violation in electron scattering.
\newblock {\em Phys. Rev. Lett.}, 108:112502, Mar 2012.

\bibitem{reinhard2013}
P.-G. Reinhard, J.~Piekarewicz, W.~Nazarewicz, B.~K. Agrawal, N.~Paar, and
  X.~Roca-Maza.
\newblock Information content of the weak-charge form factor.
\newblock {\em Phys. Rev. C}, 88:034325, Sep 2013.

\bibitem{erler2013}
J.~Erler, C.~J. Horowitz, W.~Nazarewicz, M.~Rafalski, and P.-G. Reinhard.
\newblock Energy density functional for nuclei and neutron stars.
\newblock {\em Phys. Rev. C}, 87:044320, 2013.

\bibitem{kortelainen2010}
M.~Kortelainen.
\newblock Nuclear energy density optimization.
\newblock {\em Phys.~Rev.~C}, 82:024313, 2010.

\bibitem{lunney2003}
D.~Lunney, J.~M. Pearson, and C.~Thibault.
\newblock Recent trends in the determination of nuclear masses.
\newblock {\em Rev. Mod. Phys.}, 75:1021--1082, Aug 2003.


\bibitem{localeft}
A.~Gezerlis, I.~Tews, E.~Epelbaum, S.~Gandolfi, K.~Hebeler, A.~Nogga and A.~Schwenk,
  %``Quantum Monte Carlo Calculations with Chiral Effective Field Theory Interactions,'
\newblock Quantum Monte Carlo Calculations with Chiral Effective Field Theory Interactions.
\newblock{Phys.\ Rev.\ Lett.\  {\bf 111} (2013) 032501.}

\bibitem{eft1}
  E.~Epelbaum and U.~-G.~Meissner,
\newblock Chiral dynamics of few- and many-nucleon systems.
\newblock Ann.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 62}, 159 (2012).
  [arXiv:1201.2136 [nucl-th]].
  %%CITATION = ARXIV:1201.2136;%%
  %15 citations counted in INSPIRE as of 29 Oct 2013


\bibitem{eft2}
  C.~Ordonez, L.~Ray and U.~van Kolck,
  \newblock The Two nucleon potential from chiral Lagrangians.
  \newblock Phys.\ Rev.\ C {\bf 53}, 2086 (1996).
 % [hep-ph/9511380].
  %%CITATION = HEP-PH/9511380;%%
  %437 citations counted in INSPIRE as of 29 Oct 2013
\bibitem{eft3}
R.~Machleidt and D.~R.~Entem,
\newblock Chiral effective field theory and nuclear forces.
\newblock Phys.\ Rept.\  {\bf 503}, 1 (2011).

\bibitem{achimJason_sm}
T.~Otsuka, T.~Suzuki, J.~D.~Holt, A.~Schwenk and Y.~Akaishi,
\newblock Three-body forces and the limit of oxygen isotopes.
\newblock Phys.\ Rev.\ Lett.\  {\bf 105}, 032501 (2010).

\bibitem{achimKai_nm}
I.~Tews, T.~Krueger, K.~Hebeler and A.~Schwenk,
\newblock Neutron matter at next-to-next-to-next-to-leading order in chiral effective field theory.
\newblock Phys.\ Rev.\ Lett.\  {\bf 110}, 032504 (2013).


\bibitem{schatz1998}
H.~Schatz, A.~Aprahamian, J.~G嗷res, M.~Wiescher, T.~Rauscher, J.F. Rembges,
  F.-K. Thielemann, B.~Pfeiffer, P.~M{\o}ller, K.-L. Kratz, H.~Herndl, B.A.
  Brown, and H.~Rebel.
\newblock rp-process nucleosynthesis at extreme temperature and density
  conditions.
\newblock {\em Phys.~Rep.}, 294:167, 1998.

\bibitem{langanke2001}
K.~Langanke and M.~Wiescher.
\newblock Nuclear reactions and stellar processes.
\newblock {\em Rep.~Prog.~Phys.}, 64:1657, 2001.

%****************************

\bibitem{Bogner:2007rx}
S.~K. Bogner et~al.
\newblock {Convergence in the no-core shell model with low-momentum two-nucleon
  interactions}.
\newblock {\em Nucl. Phys. A}, 801:24, 2008.

\bibitem{Bogner:2009un}
K.Hebeler, S.~K. Bogner, R.~J. Furnstahl, A.~Nogga, and A.~Schwenk.
\newblock {Improved nuclear matter calculations from chiral low-momentum interactions}.
\newblock Phys.Rev.C83:031301,2011.


\bibitem{Anderson:2010aq}
E.~R. Anderson, S.~K. Bogner, R.~J. Furnstahl, and R.~J. Perry.
\newblock {Operator Evolution via the Similarity Renormalization Group I: The
  Deuteron}.
\newblock  Phys.Rev.C82:054001,2010.

\bibitem{Bogner:2008kj}
S.~K. Bogner, R.~J. Furnstahl, and L.~Platter.
\newblock {Density Matrix Expansion for Low-Momentum Interactions}.
\newblock {\em Eur. Phys. J. A}, 39:219, 2009.

\bibitem{Gebremariam:2009ff}
B.~Gebremariam, T.~Duguet, and S.~K. Bogner.
\newblock {An improved density matrix expansion for spin-unsaturated nuclei}.
\newblock 2009, arXiv.0910.4979.

\bibitem{Gebremariam:2010ni}
B.~Gebremariam, S.~K. Bogner, and T.~Duguet.
\newblock {Microscopically-constrained Fock energy density functionals from
  chiral effective field theory. I. Two- nucleon interactions}.
\newblock  Nucl.Phys.A851:17,2011

%\bibitem{Bogner:2011kp}
%S.K. Bogner, R.J. Furnstahl, H.~Hergert, M.~Kortelainen, P.~Maris, et~al.
%\newblock {Testing the density matrix expansion against ab initio calculations
 % of trapped neutron drops}.
%\newblock {\em Phys.Rev.}, C84:044306, 2011.

\bibitem{bogner2011b}
S.K. Bogner, R.J. Furnstahl, H. Hergert, M. Kortelainen, P. Maris, M. Stoitsov, J.P. Vary
\newblock { Testing the density matrix expansion against ab initio calculations of trapped neutron drops}.
\newblock Phys. Rev. C 84:044306 (2011) 




\bibitem{Stoitsov:2010ha}
M. Stoitsov, M. Kortelainen, S. K. Bogner, T. Duguet, R. J. Furnstahl, B. Gebremariam, N. Schunck,
\newblock {Microscopically-based energy density functionals for nuclei using
  the density matrix expansion: Implementation and pre-optimization}.
\newblock Phys.Rev.C82:054307,2010





\bibitem{bogner2010a}
B. Gebremariam, S. K. Bogner, T. Duguet
\newblock { Symbolic computation of the Hartree-Fock energy from a chiral EFT three-nucleon interaction at N$^2$LO}.
\newblock Comput.Phys.Commun.181:1167-1177,2010


\bibitem{bogner2010b}
S.K. Bogner, R.J. Furnstahl, A. Schwenk
\newblock {From low-momentum interactions to nuclear structure }.
\newblock Prog.Part.Nucl.Phys.65:94-147,2010


\bibitem{bogner2008a}
A. Deltuva, A. C. Fonseca, S. K. Bogner
\newblock {Low-momentum interactions in three- and four-nucleon scattering }.
\newblock  Phys.Rev.C77:024002,2008


\bibitem{bogner2008b}
E. Anderson, S.K. Bogner, R.J. Furnstahl, E.D. Jurgenson, R.J. Perry, A. Schwenk
\newblock {Block Diagonalization using SRG Flow Equations }.
\newblock  Phys.Rev.C77:037001,2008

\bibitem{DietrichOPE}
 S.~K.~Bogner and D.~Roscher,
\newblock High-momentum tails from low-momentum effective theories.
\newblock  Phys.\ Rev.\ C {\bf 86}, 064304 (2012).

\bibitem{bogner2008c}
E.D. Jurgenson, S.K. Bogner, R.J. Furnstahl, R.J. Perry
\newblock {Decoupling in the Similarity Renormalization Group for Nucleon-Nucleon Forces }.
\newblock Phys.Rev.C78:014003,2008


\bibitem{bogner2008d}
S. K. Bogner, R. J. Furnstahl, P. Maris, R. J. Perry, A. Schwenk, J. P. Vary
\newblock {Convergence in the no-core shell model with low-momentum two-nucleon interactions }.
\newblock Nucl.Phys.A801:21-42,2008


\bibitem{bogner2008e}
S.K. Bogner, R.J. Furnstahl, R.J. Perry
\newblock {Three-Body Forces Produced by a Similarity Renormalization Group Transformation in a Simple Model }.
\newblock AnnalsPhys.323:1478-1501,2008


\bibitem{bogner2007a}
S. Ramanan, S. K. Bogner, R. J. Furnstahl
\newblock {Weinberg Eigenvalues and Pairing with Low-Momentum Potentials }.
\newblock  Nucl.Phys.A797:81-93,2007


\bibitem{bogner2009a}
S.K. Bogner, R.J. Furnstahl, L. Platter
\newblock {Density Matrix Expansion for Low-Momentum Interactions }.
\newblock Eur.Phys.J.A 39:219, 2009


\bibitem{mhj2013h} N.~Tsunoda, K.~Takayanagi, M.~Hjorth-Jensen and T.~Otsuka,
\newblock { Multi-shell effective interactions}, 
\newblock {\em Physical Review C},  submitted and arXiv1310.7107


\bibitem{mhj2013f} V.\ M.\ Bader, A.\ Gade, D.\ Weisshaar, T.\ Baugher, D.\ Bazin, J.\ S.\ Berryman, B.\ A.\ Brown, A.\ Ekstr\"om, M.\ Hjorth-Jensen, S.\ R.\ Stroberg, W.\ B.\ Walters, K.\ Wimmer, and R.\ Winkler, 
\newblock { Quadrupole collectivity in neutron-deficient Sn nuclei: $^{104}$Sn and the role of proton excitations}, 
\newblock {\em Physical Review C},  88:in press, xxx(R) (2013).

\bibitem{mhj2013e}  A.~Ekstr\"om, G. Baardsen, C.~Forss\'en, G.~Hagen, M.~Hjorth-Jensen, G.~R.~Jansen, R.~Machleidt, W.~Nazarewicz, T.~Papenbrock, J.~Sarich, and S.~M.~Wild, 
\newblock { An optimal chiral interaction at next-to-next-to leading order}, 
\newblock {\em Physical Review Letters},  110:192502 (2013).


\bibitem{mhj2013d}Lepailleur, A. and Sorlin, O. and Caceres, L. and Bastin, B. and Borcea, C. and Borcea, R. and Brown, B. A. and Gaudefroy, L. and Gr\'evy, S. and Grinyer, G. F. and Hagen, G. and Hjorth-Jensen, M. and Jansen, G. R. and Llidoo, O. and Negoita, F. and de Oliveira, F. and Porquet, M.-G. and Rotaru, F. and Saint-Laurent, M.-G. and Sohler, D. and Stanoiu, M. and Thomas, J. C.,
\newblock { Spectroscopy of $^{26}$F to Probe Proton-Neutron Forces Close to the Drip Line}, 
\newblock {\em Physical Review Letters},  110:082502 (2013).

\bibitem{mhj2013c}D. D. DiJulio, J. Cederkall, C. Fahlander, A. Ekstr\"om, M. Hjorth-Jensen, M. Albers, V. Bildstein, A. Blazhev, I. Darby, T. Davinson, H. De Witte, J. Diriken, Ch. Fransen, K. Geibel, R. Gernhäuser, A. Görgen, H. Hess, K. Heyde, J. Iwanicki, R. Lutter, P. Reiter, M. Scheck, M. Seidlitz, S. Siem, J. Taprogge, G. M. Tveten, J. Van de Walle, D. Voulot, N. Warr, F. Wenander, and K. Wimmer
\newblock { Coulomb excitation of $^{107}$In}, 
\newblock {\em Physical Review C},  87:017301 (2013).



\bibitem{mhj2013b} C.~Forssen, G.~Hagen, M.~Hjorth-Jensen, W.~Nazarewicz, and J.~Rotureau,
\newblock { Living on the edge of stability, the limits of the nuclear landscape}, 
\newblock {\em Physica Scripta},  T152:014022 (2013).

\bibitem{mhj2013a} Liddick, S. N. and Abromeit, B. and Ayres, A. and Bey, A. and Bingham, C. R. and Brown, B. A. and Cartegni, L. and Crawford, H. L. and Darby, I. G. and Grzywacz, R. and Ilyushkin, S. and Hjorth-Jensen, M. and Larson, N. and Madurga, M. and Miller, D. and Padgett, S. and Paulauskas, S. V. and Rajabali, M. M. and Rykaczewski, K. and Suchyta, S.,
\newblock { Low-energy level schemes of ${}^{\mathbf{66},\mathbf{68}}$Fe and inferred proton and neutron excitations across $\mathbf{Z}=\mathbf{28}$ and $\mathbf{N}=\mathbf{40}$}, 
\newblock {\em Physical Review C},  87:014325, 2013.




\bibitem{mhj2012e}  D. D. DiJulio, J. Cederkall, C. Fahlander, A. Ekstr\"om, M. Hjorth-Jensen, M. Albers, V. Bildstein,
A. Blazhev, I. Darby, T. Davinson, H. De Witte, J. Diriken, Ch. Fransen, K. Geibel, R. Gernh\"auser,
A. G\"orgen, H. Hess, J. Iwanicki, R. Lutter, P. Reiter, M. Scheck, M. Seidlitz, S. Siem, J. Taprogge,
G.M. Tveten, J. Van de Walle, D. Voulot, N. Warr, F. Wenander, and K. Wimmer,
\newblock { Excitation strengths in $^{109}$Sn: Single-neutron and collective excitations near $^{100}$Sn}, 
\newblock {\em Physical Review C},  86:031302(R), 2012.

\bibitem{mhj2012d} D. D. DiJulio, J. Cederkall, C. Fahlander, A. Ekstr\"om, M. Hjorth-Jensen, M. Albers, V. Bildstein,
A. Blazhev, I. Darby, T. Davinson, H. De Witte, J. Diriken, Ch. Fransen, K. Geibel, R. Gernh\"auser,
A. G\"orgen, H. Hess, J. Iwanicki, R. Lutter, P. Reiter, M. Scheck, M. Seidlitz, S. Siem, J. Taprogge,
G.M. Tveten, J. Van de Walle, D. Voulot, N. Warr, F. Wenander, and K. Wimmer,
\newblock { Coulomb excitation of $^{107}$Sn}, 
\newblock {\em European Journal of Physics A}, 48:105,  2012.


\bibitem{mhj2012c}
Gaute Hagen, Morten Hjorth-Jensen, Gustav Ragnar Jansen, Ruprecht Machleidt, and Thomas Papenbrock
\newblock { Evolution of shell structure in neutron-rich calcium isotopes }, 
\newblock {\em Physical Review Letters}, 109:032502, 2012.

\bibitem{mhj2012b}
Gaute Hagen, Morten Hjorth-Jensen, Gustav Ragnar Jansen, Ruprecht Machleidt, and Thomas Papenbrock
\newblock { Continuum effects and three-nucleon forces in neutron-rich
           oxygen isotopes}, 
\newblock {\em Physical Review Letters}, 108:242501, 2012.


\bibitem{mhj2012a}
Torres, D. A. and Kumbartzki, G. J. and Sharon, Y. Y. and Zamick,
	L. and Manning, B. and Benczer-Koller, N. and Speidel, K.-H. and
	Ahn, T. and Anagnostatou, V. and Elvers, M. and Goddard, P. and Heinz,
	A. and Ilie, G. and Radeck, D. and Savran, D. and Werner, V. and
	G\"urdal, G. and Taylor, M. J. and Maier-Komor, P. and Hjorth-Jensen,
	M. and Robinson, S. J. Q.
\newblock { Measurement of the ${}^{96}$Ru $g({4}_{1}^{+})$ factor and its nuclear
	structure interpretation}.
\newblock {\em Physical Review C}, 85:017305, 2012.


\bibitem{mhj2011f}
Torres, D. A. and Kumbartzki, G. J. and Sharon, Y. Y. and Zamick,
	L. and Manning, B. and Benczer-Koller, N. and G\"urdal, G. and Speidel,
	K.-H. and Hjorth-Jensen, M. and Maier-Komor, P. and Robinson, S.
	J. Q. and Ahn, T. and Anagnostatou, V. and Elvers, M. and Goddard,
	P. and Heinz, A. and Ilie, G. and Radeck, D. and Savran, D. and Werner,
	V.
\newblock { First $g$-factor measurements of the ${2}_{1}^{+}$ and the ${4}_{1}^{+}$
	states of radioactive ${}^{100}$Pd}.
\newblock {\em Physical Review C}, 84:044327, 2011.


\bibitem{mhj2011e}
Naofumi Tsunoda, Takaharu Otsuka, Koshiroh Tsukiyama, and Morten Hjorth-Jensen
\newblock { Renormalization persistency of the tensor force
           in nuclei}.
\newblock {\em Physical Review C}, 84:044322, 2011.


\bibitem{mhj2011d}
\O yvind Jensen, Gaute Hagen, Morten Hjorth-Jensen, Alex Boyd Brown, and Alexandra Gade
\newblock { Quenching of spectroscopic factors for proton removal
           in oxygen isotopes}, 
\newblock {\em Physical Review Letters}, 107:032501, 2011.


\bibitem{mhj2011b}
Gustav Ragnar Jansen, Morten Hjorth-Jensen, Gaute Hagen, and Thomas Papenbrock,
\newblock { Toward open-shell nuclei with coupled-cluster theory}.
\newblock {\em Physical Review C}, 83:054306, 2011.

\bibitem{mhj2011a}
Morten Hjorth-Jensen.
\newblock { The Carbon Challenge}.
\newblock {\em Physics}, 4:38, 2011.


\bibitem{PhysRevC.83.021305}
\O{}. Jensen, G.~Hagen, M.~Hjorth-Jensen, and J.~S. Vaagen.
\newblock { Closed-shell properties of $^{24}$O with ab initio
  coupled-cluster theory}.
\newblock {\em Physical Review C}, 83:021305, 2011.

\bibitem{PhysRevC.83.024315}
Angelo Signoracci, B.~Alex Brown, and Morten Hjorth-Jensen.
\newblock { Renormalized interactions with a realistic single-particle
  basis}.
\newblock {\em Physical Review C}, 83:024315, 2011.

\bibitem{Brown2011}
Boyd~Alexander Brown, Angelo Signoracci, and Morten Hjorth-Jensen.
\newblock { Configuration interactions constrained by energy density
  functionals}.
\newblock {\em Physics Letters B}, 695:507, 2011.

\bibitem{Atanasova2010b}
L.~Atanasova, Dimiter Balabanski, S.~K. Chamoli, M.~Hass, G.~S. Simpson,
  D.~Bazzacco, F.~Becker, P.~Bednarczyk, G.~Benzoni, N.~Blasi, A.~Blazhev,
  A.~Bracco, C.~Brandau, L.~Caceres, F.~Camera, F.~C.~L. Crespi, P.~Detistov,
  P.~Doornenbal, C.~Fahlander, E.~Farnea, G.~Georgiev, J.~Gerl, K.~A.
  Gladnishki, M.~Gorska, J.~Grebosz, R.~Hoischen, G.~Ilie, M.~Ionescu-Bujor,
  A.~Iordachescu, A.~Jungclaus, G.~Bianco, M.~Kmiecik, I.~Kojouharov, N.~Kurz,
  S.~Lakshmi, R.~Lozeva, A.~Maj, D.~Montanari, G.~Neyens, M.~Pfuetzner,
  S.~Pietri, Z.~Podolyak, W.~Prokopowicz, D.~Rudolph, G.~Rusev, T.~Saito,
  A.~Saltarelli, H.~Schaffner, R.~Schwengner, S.~Tashenov, J.~J.
  Valiente-Dobon, N.~Vermeulen, J.~Walker, E.~Werner-Malento, O.~Wieland, H.~J.
  Wollersheim, H.~Grawe, and Morten Hjorth-Jensen.
\newblock { $g$-factor measurements at RISING: The cases of $^{127}$Sn and
  $^{128}$Sn}.
\newblock {\em Europhysics letters}, 91:42001, 2010.

\bibitem{Darby2010}
I.~Darby, R.~Grzywacz, J.~C. Batchelder, C.~R. Bingham, L.~Cartegni, C.~J.
  Gross, Morten Hjorth-Jensen, D.~T. Joss, S.~N. Liddick, W.~Nazarewicz,
  S.~Padgett, R.~D. Page, Thomas Papenbrock, M.~M. Rajabali, J.~Rotureau, and
  K.~P. Rykaczewski.
\newblock { Orbital Dependent Nucleonic Pairing in the Lightest Known
  Isotopes of Tin}.
\newblock {\em Physical Review Letters}, 105:162502, 2010.

\bibitem{Ekstrom2010}
A.~Ekstr\o{}m, Joakim Cederkall, Claes Fahlander, Morten Hjorth-Jensen, Torgeir
  Engeland, Peter Butler, P.~A. Butler, T.~Davinson, J.~Eberth, F.~Finke,
  Andreas Gorgen, M.~Gorska, A.~M. Hurst, O.~Ivanov, J.~Iwanicki, U.~Koster,
  B.~A. Marsh, J.~Mierzejewski, P.~Reiter, Sunniva Siem, G.~Sletten,
  I.~Stefanescu, Gry~Merete Tveten, J.~Van~de Walle, D.~Voulot, N.~Warr,
  D.~Weisshaar, F.~Wenander, and M.~Zielinska.
\newblock { Coulomb excitation of the odd-odd isotopes $^{106}$In and
  $^{108}$In}.
\newblock {\em European Physical Journal A}, 44:355, 2010.

\bibitem{Hagen2010b}
Gaute Hagen, Thomas Papenbrock, and Morten Hjorth-Jensen.
\newblock { Ab Initio Computation of the $^{17}$F Proton Halo State and
  Resonances in $A=17$ Nuclei}.
\newblock {\em Physical Review Letters}, 104:182501, 2010.

\bibitem{Hjorth-Jensen2010}
Morten Hjorth-Jensen, David~Jarvis Dean, G.~Hagen, and Simen Kvaal.
\newblock { Many-body interactions and nuclear structure}.
\newblock {\em Journal of Physics G: Nuclear and Particle Physics}, 37:064035,
  2010.

\bibitem{Hoteling2010}
N.~Hoteling, C.~Chiara, R.~Broda, W.~B. Walters, R.~V.~F. Janssens, Morten
  Hjorth-Jensen, M.~B. Carpenter, B.~Fornal, A.~A. Hecht, W.~Krolas,
  T.~Lauritsen, T.~Pawlat, D.~Seweryniak, X.~Wang, A.~Wohr, J.~Wrzesinski, and
  S.~Zhu.
\newblock { Structure of $^{60,62}$Fe and the onset of $\nu g(9/2)$
  occupancy}.
\newblock {\em Physical Review C}, 82:044305, 2010.

\bibitem{Otsuka2010}
Takahuro Otsuka, Toshio Suzuki, Micho Honma, Yutaka Utsuno, Naofumi Tsunoda,
  Koshiroh Tsukiyama, and Morten Hjorth-Jensen.
\newblock { Novel Features of Nuclear Forces and Shell Evolution in Exotic
  Nuclei}.
\newblock {\em Physical Review Letters}, 104:012501, 2010.

\bibitem{Barbieri2009a}
C.~Barbieri and Morten Hjorth-Jensen.
\newblock { Quasiparticle and quasihole states of nuclei around $^{56}$Ni}.
\newblock {\em Physical Review C}, 79:064313, 2009.

\bibitem{Ekstrom2009}
A.~Ekstr\o{}m, J.~Cederkall, D.~D. DiJulio, C.~Fahlander, Morten Hjorth-Jensen,
  A.~Blazhev, B.~Bruyneel, P.~A. Butler, T.~Davinson, J.~Eberth, C.~Fransen,
  K.~Geibel, H.~Hess, O.~Ivanov, J.~Iwanicki, O.~Kester, J.~Kownacki,
  U.~Koster, B.~A. Marsh, P.~reiter, M.~Scheck, B.~Siebeck, Sunniva Siem,
  I.~Stefanescu, Heidi~Kristine Toft, Gry~Merete Tveten, J.~Van~de Walle,
  D.~Voulot, N.~Warr, D.~Weisshaar, F.~Wenander, K.~Wrzosek, and M.~Zielinska.
\newblock { Electric quadrupole moments of the $2_1^+$ states in
  $^{100,102,104}$Cd}.
\newblock {\em Physical Review C}, 80:054302, 2009.

\bibitem{Hagen2009a}
G.~Hagen, T.~Papenbrock, D.~J. Dean, Morten Hjorth-Jensen, and B.~V. Asokan.
\newblock { Ab initio computation of neutron-rich oxygen isotopes}.
\newblock {\em Physical Review C}, 80:021306, 2009.

\bibitem{Honma2009}
Micho Honma, Takahuro Otsuka, T.~Mizusaki, and Morten Hjorth-Jensen.
\newblock { New effective interaction for $f(5)pg(9)$-shell nuclei}.
\newblock {\em Physical Review C}, 80:064323, 2009.

\bibitem{Tsukiyama2009}
Koshiroh Tsukiyama, Morten Hjorth-Jensen, and Gaute Hagen.
\newblock { Gamow shell-model calculations of drip-line oxygen isotopes}.
\newblock {\em Physical Review C}, 80:051301(R), 2009.

\bibitem{Dean2008a}
David~J. Dean, Gaute Hagen, Morten Hjorth-Jensen, and Thomas Papenbrock.
\newblock { Computational aspects of nuclear coupled-cluster theory}.
\newblock {\em Computational Science and Discovery}, 1:015008, 2008.

\bibitem{Dean2008b}
David~J. Dean, Gaute Hagen, Morten Hjorth-Jensen, Thomas Papenbrock, and Achim
  Schwenk.
\newblock { Comment on ``Ab initio study of $^{40}$Ca with an
  importance-truncated no-core shell model}.
\newblock {\em Physical Review Letters}, 101:119201, 2008.

\bibitem{Ekstrom2008}
A.~Ekstr\o{}m, J.~Cederkall, C.~Fahlander, Morten Hjorth-Jensen, F.~Ames, P.~A.
  Butler, T.~Davinson, J.~Eberth, F.~Fincke, A.~Gorgen, M.~Gorska, D.~Habs,
  A.~M. Hurst, M.~Huyse, O.~Ivanov, J.~Iwanicki, O.~Kester, U.~Koster, B.~A.
  Marsh, J.~Mierzejewski, P.~Reiter, H.~Scheit, D.~Schwalm, Sunniva Siem,
  G.~Sletten, I.~Stefanescu, Gry~Merete Tveten, J.~V. de~Walle, P.~Van~Duppen,
  D.~Voulot, N.~Warr, D.~Weisshaar, F.~Wenander, and M.~Zielinska.
\newblock { $0_1^+\rightarrow 2_1^+$ transition strengths in $^{106}$Sn and
  $^{108}$Sn}.
\newblock {\em Physical Review Letters}, 101:01250, 2008.

\bibitem{Hagen2008}
Gaute Hagen, Thomas Papenbrock, David~J. Dean, and Morten Hjorth-Jensen.
\newblock { Medium-Mass Nuclei from Chiral Nucleon-Nucleon Interactions}.
\newblock {\em Physical Review Letters}, 101:092502, 2008.

\bibitem{Hoteling2008}
N.~Hoteling, W.~B. Walters, R.~V.~F. Janssens, R.~Broda, M.~P. Carpenter,
  B.~Fornal, A.~A. Hecht, Morten Hjorth-Jensen, W.~Krolas, T.~Lauritsen,
  T.~Pawlat, D.~Seweryniak, J.~R. Stone, X.~Wang, A.~Wohr, J.~Wrzesinski, and
  S.~Zhu.
\newblock { Rotation-aligned coupling in $^{61}$Fe}.
\newblock {\em Physical Review C}, 77:044314, 2008.



\bibitem{meeting1} {\em Confrontation and Convergence in Nuclear Theory}, MHJ as organizer with Alex Brown (MSU), J.~Tostevin, Thomas Papenbrock (UTK)and R.~V.~Janssens (ANL), ECT*, Trento, Italy, July 27-31 2009.

\bibitem{meeting2} {\em First MSU-UiO-UT/ORNL school in Nuclear Physics: From Lattice QCD to the Nuclear many-body problem}, MHJ as organizer together with Alex Brown (MSU), Thomas Papenbrock (UTK) and
Witek Nazarewicz (UTK), G\aa l\aa\, Norway, January 4-9, 2010.

\bibitem{meeting3} {\em Second Uio-MSU-ORNL-UT School on Topics in Nuclear Physics: Many-Body Theory, Connections to
Experiment and Nuclear Astrophysics}, Michigan State University, USA,
January 3-7, 2011. MHJ as organizer together with Alex Brown (MSU),
Thomas Papenbrock (UTK) and Witek Nazarewicz (UTK).

\bibitem{meeting4} {\em Effective theories and the nuclear many-body problem}, workshop at ECT*, Trento, Italy, March 7-11, 2011. MHJ as organizer with Hans-Werner Hammer and Thomas Papenbrock (UTK). 

\bibitem{meeting5} {\em Biennial meeting of the Norwegian Physical Society}, Oslo, Norway, June 20-23, 2011. MHJ as the main organizer.

\bibitem{meeting6} {\em Third Uio-MSU-ORNL-UT School on Topics in Nuclear Physics: Computational Many-Body Methods}, Oak Ridge National Laboratory, USA, 
January 23-27, 2012. MHJ as organizer together with Alex Brown (MSU),
Gaute Hagen (ORNL), Thomas Papenbrock (UTK) and Witek Nazarewicz
(UTK).
\bibitem{meeting7} {\em The Extreme Matter Physics of Nuclei: From Universal Properties to Neutron-Rich Extremes}, EMMI program at GSI, Darmstadt, Germany, April 16- May 11, 2012. SB as organizer together with T. Aumann, R. Furnstahl and A. Schwenk.


\bibitem{meeting8} {\em First Nuclear Talent Course}, ECT*, Trento, Italy, June 25-July 13 2012. MHJ as main organizer and teacher, with Giuseppina Orlandini (Trento), Jacek Dobaczewski (Warsaw and Jyv\"askyl\"a) and Marek Plozcajczak (Ganil). 

\bibitem{meeting9} {\em Computational and Theoretical Advances for Exotic Nuclei in the Medium Mass Region}, INT program at the University of Washington, Seattle, WA, March 25 - April 19, 2013. SB as organizer together with C. Barbieri, T. Duguet and G. Hagen.

\bibitem{meeting10} {\em Second Nuclear Talent Course}, INT, Seattle, USA, July 1-19 2013. The teachers and main organizers were Dick Furnstahl (OSU) and Achim Schwenk (Darmstadt, Germany).  MHJ and Witek Nazarewicz (UTK and ORNL) were co-organizers. 


\bibitem{meeting11} {\em Fourth Nuclear Talent Course}, ECT*, Trento, Italy, July 1-19 2014. The teachers and main organizers are SB, Nicolas Schunck (LLNL), Dario Vretenar (Zagreb, Croatia) and Peter Ring (Munich, Germany).  MHJ and Giuseppina Orlandini are co-organizers. 




\bibitem{Glazek:1993rc}
Stanislaw~D. Glazek and Kenneth~G. Wilson.
\newblock {Renormalization of Hamiltonians}.
\newblock {\em Phys. Rev. D}, 48:5863, 1993.

\bibitem{Wegner:1994}
F.~Wegner.
\newblock {\em Ann.\ Phys.\ (Leipzig)}, 3:77, 1994.

\bibitem{Bogner:2006pc}
S.~K. Bogner, R.~J. Furnstahl, and R.~J. Perry.
\newblock Similarity renormalization group for nucleon-nucleon interactions.
\newblock {\em Phys. Rev. C}, 75:061001, 2007.

\bibitem{Bogner:2007jb}
S.~K. Bogner, R.~J. Furnstahl, R.~J. Perry, and A.~Schwenk.
\newblock {Are low-energy nuclear observables sensitive to high- energy phase
  shifts?}
\newblock {\em Phys. Lett. B}, 649:488, 2007.


\bibitem{Jurgenson:2008jp}
E.~D. Jurgenson and R.~J. Furnstahl.
\newblock {Similarity Renormalization Group Evolution of Many-Body Forces in a
  One-Dimensional Model}.
\newblock {\em Nucl. Phys. A}, 818:152, 2009.

\bibitem{Jurgenson:2009qs}
E.~D. Jurgenson, P.~Navratil, and R.~J. Furnstahl.
\newblock {Evolution of Nuclear Many-Body Forces with the Similarity
  Renormalization Group}.
\newblock {\em Phys. Rev. Lett.}, 103:082501, 2009.


\bibitem{bognerSRG}
S.~K. Bogner.
\newblock Similarity renormalization group methods in nuclear physics.
\newblock \url{http://theory.gsi.de/Heraeus-410/Talks/Bogner.pdf}, 2008.
\newblock Talk given at the WE-Heraeus program ``Ab-initio Nuclear Structure -
  Where Do We Stand''.

\bibitem{white:7472}
Steven~R. White.
\newblock Numerical canonical transformation approach to quantum many-body
  problems.
\newblock {\em J. Chem. Phys.}, 117(16):7472, 2002.



\bibitem{Hergert:2013uja}
H.~Hergert, S.~Binder, A.~Calci, J.~Langhammer, and R.~Roth.
\newblock {Ab Initio Calculations of Even Oxygen Isotopes with Chiral Two- Plus
  Three-Nucleon Interactions}.
\newblock {\em Phys.Rev.Lett.}, 110:242501, 2013.

\bibitem{Kehrein:2006}
S.~Kehrein.
\newblock {\em The Flow Equation Approach to Many-Particle Systems}.
\newblock Springer, Berlin, 2006.

\bibitem{Lesinski:2008cd}
T.~Lesinski, T.~Duguet, K.~Bennaceur, and J.~Meyer.
\newblock {Non-empirical pairing energy density functional. First order in the
  nuclear plus Coulomb two-body interaction}.
\newblock {\em Eur. Phys. J. A}, 40:121, 2009.

\bibitem{Drut:2009ce}
J.~E. Drut, R.~J. Furnstahl, and L.~Platter.
\newblock {Toward ab initio density functional theory for nuclei}.
\newblock {\em Prog. Part. Nucl. Phys.}, 64:120, 2010.

\bibitem{Duguet:2009gc}
T.~Duguet and T.~Lesinski.
\newblock {Non-empirical nuclear energy functionals, pairing gaps and odd-even
  mass differences}.
\newblock {\em AIP Conf. Proc.}, 1165:243, 2009.


\bibitem{Kaiser:2003uh}
N.~Kaiser.
\newblock Nuclear energy density functional from chiral pion-nucleon dynamics:
  Isovector spin-orbit terms.
\newblock {\em Phys. Rev. C}, 68:014323, 2003.

\bibitem{Kaiser:2009me}
N.~Kaiser and W.~Weise.
\newblock {Nuclear energy density functional from chiral pion-nucleon dynamics
  revisited}.
\newblock {\em Nucl. Phys.}, A836:256, 2010.

\bibitem{Kaiser:2010pp}
N.~Kaiser.
\newblock {Nuclear energy density functional from chiral pion-nucleon dynamics:
  Isovector terms}.
\newblock {\em Eur. Phys. J.}, A45:61, 2010.


\bibitem{Negele:1972zp}
J.~W. Negele and D.~Vautherin.
\newblock Density-matrix expansion for an effective nuclear hamiltonian.
\newblock {\em Phys. Rev. C}, 5:1472, 1972.

\bibitem{Negele:1975zz}
J.~W. Negele and D.~Vautherin.
\newblock Density-matrix expansion for an effective nuclear hamiltonian. 2.
\newblock {\em Phys. Rev. C}, 11:1031, 1975.


\bibitem{kvaal2009}
Simen Kvaal.
\newblock Harmonic oscillator eigenfunction expansions, quantum dots, and
  effective interactions.
\newblock {\em Phys.~Rev.~B}, 80:045321, 2009.

\bibitem{dick}
 S.~N.~More, A.~Ekstrom, R.~J.~Furnstahl, G.~Hagen and T.~Papenbrock,
 \newblock Universal properties of infrared oscillator basis extrapolations.
 \newblock Phys.\ Rev.\ C {\bf 87}, 044326 (2013).



\bibitem{lieb1983} E.~H.~Lieb, Int.~J.~Qauntum Chem.~{ 24}, 243 (1983).


\bibitem{teale2009} A.~M.~Teale, S.~Coriani, and T.~Helgaker, J.~Chem.~Phys.~{ 130}, 104111 (2009).

\bibitem{drummond2008} N.~D.~Drummond, R.~J.~Needs, A.~Sorouri, and W.~M.~C.~Foulkes, Phys.~Rev.~B { 78}, 125106 (2008). 

\bibitem{UFG} 
  S.~Giorgini, L.~P.~Pitaevskii and S.~Stringari,
\newblock Theory of ultracold atomic Fermi gases.
\newblock  Rev.\ Mod.\ Phys.\  {\bf 80}, 1215 (2008).
\end{thebibliography}





